Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
later
fix typos

Given the intrinsic greediness of hierarchical clustering, 
and the fact that EHC does only local decisions, it is 
sensitive against noise and we cannot expect optimal solutions.

@@

As classical fusion, CCFusion does not provide and lower bound on the objective and 
has no sound stopping condition.
For later we set a maximal number of iterations and maximal number of iteration without improvement.

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition a feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution than there must exists $y''$ with 
$\sum_{e\in E} w_ey_e'' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e'' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}

Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
become tractable.

>>>>

Given the intrinsic greediness of hierarchical clustering, 
EHC is sensitive against noise and we cannot expect optimal solutions.

@@

As classical fusion, CCFusion does not provide and lower bound on the objective and 
has no sound stopping condition.
For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition a feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution than there must exists $y''$ with 
$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}

Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~\ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
become tractable.
